Covariate Analysis of ROSMAP Reprocessed counts

### 2020-12-15 code/2020_12_09_ROSMAP_FullCohort_Regress_hg38.Rmd
recommit

```
Dorsolateral prefrontal cortex of `r dim(COUNT)[2]` subjects from the ROS and MAP cohorts are used for the analysis. Following sample are removed due to missing metadata `r paste(removedIDs, collapse = ',')`

@@

CODE <- syn_temp$store(synapseclient$Folder(name = "ROSMAP", parentId = parentId))

@@

createAndKnitToFolderEntityClient(file = "ROSMAP_Regress_hg38.Rmd",
                                          parentId ="syn21277617",
                                          folderName = 'ROSMAP')

>>>>

```
Dorsolateral prefrontal cortex of `r dim(COUNT)[2]` subjects from the ROS and MAP cohorts are used for the analysis. Following sample are removed due to missing metadata

@@

CODE <- syn_temp$store(synapseclient$Folder(name = folderName, parentId = parentId))

@@

createAndKnitToFolderEntityClient(file = "2020_12_09_ROSMAP_FullCohort_Regress_hg38.Rmd",
                                          parentId ="syn23640229",
                                          folderName = 'Full_RosMap_OldCode')
